A Technique for Inter-Retailer Recommendations

### 2014-06-12 paper2/paper.tex
Add images of representative items for concepts

This report is organized as follows. In the next next section we describe our
dataset and some simple preprocessing that was performed. Next, we outline an
experiment used to simulate the inter-retailer recommendation problem. This is
followed by a section that explains and justifies our evaluation metrics.
Several pages are then dedicated to the details of a novel latent feature
algorithm along with two nontrivial primarily content-based, baseline
recommenders. We then summarize the results of our experiments with these
recommenders along with several additional baseline algorithms.

@@

@@

\begin{figure}[!htbp]
    \centering
    \includegraphics[width=1.0\textwidth]{PopularityHistogram.png}
	\caption{The top 25 most popular items and how many times they appear in
    recommendations. Here we compare the distribution of gold-standard
    recommendations (red) to the recommendations predicted by the
    $LatentFeatureRecommender$ with (blue) and without (yellow) popularity. The
    yellow bars are small and barely visible.}
    \label{fig:PopularityHistogram}
\end{figure}

>>>>

In this report. . . . (BREIFLY OUTLINE THE PAPER HERE.)

@@

Figures 1 and 2 show the top and bottom most relevant items for two of the sixteen
concepts learned for the Women's Dresses category. Note that concepts learned by
SVD range from positive to negative, representing the two extremes of the
concept.

\begin{figure}
\centering
\begin{subfigure}{.18\textwidth}
\centering
\includegraphics[width=\linewidth]{concepts/concept1_pos1.jpg}
\label{fig:sub1}
\end{subfigure}%
\begin{subfigure}{.18\textwidth}
\centering
\includegraphics[width=\linewidth]{concepts/concept1_pos2.jpg}
\label{fig:sub2}
\end{subfigure}
\begin{subfigure}{.18\textwidth}
\centering
\includegraphics[width=\linewidth]{concepts/concept1_pos3.jpg}
\label{fig:sub2}
\end{subfigure}
\begin{subfigure}{.18\textwidth}
\centering
\includegraphics[width=\linewidth]{concepts/concept1_pos4.jpg}
\label{fig:sub2}
\end{subfigure}
\begin{subfigure}{.18\textwidth}
\centering
\includegraphics[width=\linewidth]{concepts/concept1_pos5.jpg}
\label{fig:sub2}
\end{subfigure}
\subcaption{The top 5 items, representing the positive direction}

\centering
\begin{subfigure}{.18\textwidth}
\centering
\includegraphics[width=\linewidth]{concepts/concept1_neg1.jpg}
\label{fig:sub1}
\end{subfigure}%
\begin{subfigure}{.18\textwidth}
\centering
\includegraphics[width=\linewidth]{concepts/concept1_neg2.jpg}
\label{fig:sub2}
\end{subfigure}
\begin{subfigure}{.18\textwidth}
\centering
\includegraphics[width=\linewidth]{concepts/concept1_neg3.jpg}
\label{fig:sub2}
\end{subfigure}
\begin{subfigure}{.18\textwidth}
\centering
\includegraphics[width=\linewidth]{concepts/concept1_neg4.jpg}
\label{fig:sub2}
\end{subfigure}
\begin{subfigure}{.18\textwidth}
\centering
\includegraphics[width=\linewidth]{concepts/concept1_neg5.jpg}
\label{fig:sub2}
\end{subfigure}
\subcaption{The bottom 5 items, representing the negative direction}
\label{fig:conceptA}
\title{Figure 1: The top and bottom items representing a concept in the Dresses
category.  This concept could be characterized as modern and tiered in the
positive direction, and gown-like and elegant in the negative direction.}
\end{figure}

\begin{figure}
\centering
\begin{subfigure}{.18\textwidth}
\centering
\includegraphics[width=\linewidth]{concepts/concept2_pos1.jpg}
\label{fig:sub1}
\end{subfigure}%
\begin{subfigure}{.18\textwidth}
\centering
\includegraphics[width=\linewidth]{concepts/concept2_pos2.jpg}
\label{fig:sub2}
\end{subfigure}
\begin{subfigure}{.18\textwidth}
\centering
\includegraphics[width=\linewidth]{concepts/concept2_pos3.jpg}
\label{fig:sub2}
\end{subfigure}
\begin{subfigure}{.18\textwidth}
\centering
\includegraphics[width=\linewidth]{concepts/concept2_pos4.jpg}
\label{fig:sub2}
\end{subfigure}
\begin{subfigure}{.18\textwidth}
\centering
\includegraphics[width=\linewidth]{concepts/concept2_pos5.jpg}
\end{subfigure}
\subcaption{The top 5 items, representing the positive direction}

\centering
\begin{subfigure}{.18\textwidth}
\centering
\includegraphics[width=\linewidth]{concepts/concept2_neg1.jpg}
\label{fig:sub1}
\end{subfigure}%
\begin{subfigure}{.18\textwidth}
\centering
\includegraphics[width=\linewidth]{concepts/concept2_neg2.jpg}
\label{fig:sub2}
\end{subfigure}
\begin{subfigure}{.18\textwidth}
\centering
\includegraphics[width=\linewidth]{concepts/concept2_neg3.jpg}
\label{fig:sub2}
\end{subfigure}
\begin{subfigure}{.18\textwidth}
\centering
\includegraphics[width=\linewidth]{concepts/concept2_neg4.jpg}
\label{fig:sub2}
\end{subfigure}
\begin{subfigure}{.18\textwidth}
\centering
\includegraphics[width=\linewidth]{concepts/concept2_neg5.jpg}
\label{fig:sub2}
\end{subfigure}
\subcaption{The bottom 5 items, representing the negative direction}
\title{Figure 2: The top and bottom items representing another different Dresses
concept. This concept could be characterized as two-toned and playful in the
positive direction, and belted and light in the negative direction.}
\label{fig:conceptB} \end{figure}

@@

\begin{figure}[!htbp]
    \centering
    \includegraphics[width=1.0\textwidth]{PopularityHistogram.png}
	\caption{The top 25 most popular items and how many times they appear in
    recommendations. Here we compare the distribution of gold-standard
    recommendations (red) to the recommendations predicted by the
    $LatentFeatureRecommender$ with (blue) and without (yellow) popularity. The
    yellow bars are small and barely visible. This plot was generated on the
    Women's Dresses category.}
    \label{fig:PopularityHistogram}
\end{figure}
